Value-Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-09-25 paper/paper.tex
More plots

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-value-ordering-heuristics.pdf}

@@

    \caption{Instance by instance comparison of the basic algorithm with the tailored heuristic,
    versus weighted with restarts.}
    \label{figure:scatter}
\end{figure}

@@

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-value-ordering-heuristics.pdf}

@@

@@

    \bigskip
    \centering
    \includegraphics*{gen-graph-scatter-random.pdf}

    \caption{Instance by instance comparison of the basic algorithm with the tailored heuristic,
    versus weighted with restarts. Below, comparing instead with simple random with restarts.}
    \label{figure:scatter}
\end{figure}
